Collective behavior of Suspended Janus Particles via an Integral Equation Method

### 2022-05-08 doc/PRF2022/PRF_main.tex
updates
updated manuscript

% Bryan's Marcros
\renewcommand{\aa}{\mathbf{a}}
\newcommand{\bd}{\partial}
\newcommand{\dd}{\mathbf{d}}
\newcommand{\DD}{\mathcal{D}}
\newcommand{\eeta}{\boldsymbol{\eta}}
\newcommand{\FF}{\mathbf{F}}
\newcommand{\GG}{\mathbf{G}}
\newcommand{\JJ}{\mathbf{J}}
\newcommand{\nnu}{\boldsymbol{\nu}}
\newcommand{\ttau}{\boldsymbol{\tau}}
\newcommand{\ssigma}{\boldsymbol{\sigma}}
\newcommand{\rr}{\mathbf{r}}
\newcommand{\RR}{\mathbf{R}}
\renewcommand{\SS}{\mathbf{S}}
\newcommand{\xx}{\mathbf{x}}
\newcommand{\XX}{\mathbf{X}}
\newcommand{\uu}{\mathbf{u}}
\renewcommand{\vv}{\mathbf{v}}
\newcommand{\yy}{\mathbf{y}}
\newcommand{\pderiv}[2]{\frac{\partial #1}{\partial #2}}
\newcommand{\jump}[1]{[\![ #1 ]\!]}

@@

\subsection{Energy Calculation via Singularity Subtraction}

Suppose we split the solution to the screened Laplace boundary value problem~\eqref{eq:SL}
into smooth portion $w_i$ and singular portion $u_i$. That is, 
\begin{equation}
w_i({\bf x}) = u({\bf x}) - u_i = u({\bf x}) - \int_{\Gamma_i }\left(\pderiv{}{\nnu_\yy}
    K_0 \left(\frac{|\xx - \yy|}{\rho}\right)\right) \sigma_i(\yy) \,
    \dif s_\yy, \quad \xx \in \Gamma_i.
\end{equation}
Consider the case when $f(u)=u^2$ in~\eqref{eq:free_energy}, we can rewrite the free energy functional as

\begin{align}
\label{eq:free_energy2}
  E[u(\xx)] &= C\rho \sum_{i=1}^{N_b}\int_{\Gamma_i} u \frac{\partial u}{\partial \nnu}  \,\dif s
= C\rho\sum_{i=1}^{N_b}\int_{\Gamma_i} u \left(\frac{\partial w_i}{\partial \nnu}+\frac{\partial u_i}{\partial \nnu} \right) \, \dif s, \quad \xx\in\Gamma_i.
\end{align}
%%%
Follow the divergence theorem on the last term in the equation above and denote $g_i(x)$ as the boundary data on $\Gamma_i$, we obtain
\begin{align}
\label{eq:free_energy3}
  E[u(\xx)] &= C\rho\sum_{i=1}^{N_b}\left(\int_{\Gamma_i} u \frac{\partial w_i}{\partial \nnu} \,\dif s  + \int_{\mathbb{R}^n\setminus \overline{U}_i} \left( \nabla u \cdot\nabla u_i + u\Delta u_i\right) \,\dif \xx\right)\\
%
&= C\rho\sum_{i=1}^{N_b}\left(\int_{\Gamma_i} u \frac{\partial w_i}{\partial \nnu} \,\dif s  + \int_{\mathbb{R}^n\setminus \overline{U}_i} u\Delta u_i\,\dif \xx
+\int_{\Gamma_i}\left(u_i+\frac12\sigma_i\right)\frac{\partial u}{\partial \nnu} \,\dif s     
- \int_{\mathbb{R}^n\setminus \overline{U}_i} u_i\Delta u\,\dif \xx \right)\\
&= C\rho\sum_{i=1}^{N_b}\left(\int_{\Gamma_i} u \frac{\partial w_i}{\partial \nnu} + 
\left(g_i+\frac12\sigma_i\right)\frac{\partial u}{\partial \nnu}   \,\dif s \right), \quad \xx \in \Gamma_i.
\end{align}

@@

Similar to shear flow simulations, we then place equilibrium states of all boundary conditions \eqref{eq:bcs} in a rotating Taylor-Green Flow
\begin{equation}
\uu_\infty(\xx) = V_0 \left(-\cos({\bf e}_x\cdot\xx)\sin({\bf e}_y\cdot\xx)){\bf e}_x+\sin({\bf e}_x\cdot\xx)\cos({\bf e}_y\cdot\xx)\right){\bf e}_y.
\end{equation}
%
The magnitude of the vortex flow is controlled by the velocity scale $V_0$.

@@

% Create the reference section using BibTeX:
%\bibliography{basename of .bib file}

>>>>

% Bryan's Marcros
\renewcommand{\aa}{\mathbf{a}}
\newcommand{\bd}{\partial}
\newcommand{\dd}{\mathbf{d}}
\newcommand{\DD}{\mathcal{D}}
\newcommand{\SSS}{\mathcal{S}}
\newcommand{\eeta}{\boldsymbol{\eta}}
\newcommand{\FF}{\mathbf{F}}
\newcommand{\GG}{\mathbf{G}}
\newcommand{\JJ}{\mathbf{J}}
\newcommand{\nnu}{\boldsymbol{\nu}}
\newcommand{\ttau}{\boldsymbol{\tau}}
\newcommand{\ssigma}{\boldsymbol{\sigma}}
\newcommand{\rr}{\mathbf{r}}
\newcommand{\RR}{\mathbf{R}}
\renewcommand{\SS}{\mathbf{S}}
\newcommand{\xx}{\mathbf{x}}
\newcommand{\zz}{\mathbf{z}}
\newcommand{\XX}{\mathbf{X}}
\newcommand{\uu}{\mathbf{u}}
\renewcommand{\vv}{\mathbf{v}}
\newcommand{\yy}{\mathbf{y}}
\newcommand{\pderiv}[2]{\frac{\partial #1}{\partial #2}}
\newcommand{\jump}[1]{[\![ #1 ]\!]}

@@

\subsection{Normal Derivative of Double Layer Potential and HAP Energy}

Suppose we use the double layer potential to express the solution of \eqref{eq:SL} where the condition is $f(u)=u^2$. Then it is given by 
\begin{align}
u({\bf x}) = \DD[\sigma](\xx) = \int_\Gamma \frac{\partial G(\xx-\yy)}{\partial \nnu_\yy}\sigma(\yy)\, \dif s_\yy,
\end{align}
%
where $G(\xx)$ is the fundamental solution to the screened Laplace equation \eqref{eq:SL}.
Since the free energy functional can be written as 
\begin{align}
\label{eq:free_energy2}
  E[u(\xx)] &= C\rho \int_\Gamma u \frac{\partial u}{\partial \nnu}  \,\dif s, \quad \xx\in\Gamma_i,
\end{align}
%
we can then use the following identity to calculate this boundary equation without evaluating 
the normal derivative of the double layer potential directly.

\begin{align}
\nnu_\xx \cdot \nabla_\zz u(\zz) &=\nnu_\xx \cdot \nabla_\zz \int_\Gamma \frac{\partial G(\zz-\yy)}{\partial \nnu_\yy}\sigma(\yy) \,\dif s_\yy\\
&=\int_\Gamma \nnu_\xx\cdot \left(\nabla_\zz\nabla_\yy^\top  G(\zz-\yy)\right)\cdot \nnu_\yy\sigma(\yy)  \,\dif s_\yy\\
&=-\int_\Gamma \nnu_\xx\cdot \left(\nabla_\yy\nabla_\yy^\top G(\zz-\yy)\right)\cdot\nnu_\yy\sigma(\yy)\ \dif s_\yy\\
&=-\int_\Gamma {\bf t}_\xx\cdot\Delta_\yy G(\zz-\yy) {\bf t}_\yy \sigma(\yy)\ \dif s_\yy+\int_\Gamma({\bf t}_\xx\cdot\nabla_\yy)({\bf t}_\yy\cdot\nabla_\yy G(\zz-\yy))\sigma(\yy)\ \dif s_\yy\\
&= -\int_\Gamma {\bf t}_\xx\cdot\frac1\rho^2 G(\zz-\yy) {\bf t}_\yy \sigma(\yy)\ \dif s_\yy - 
({\bf t}_\xx\cdot\nabla_\zz)\int_\Gamma \frac{\partial G(\zz-\yy)}{\partial s_\yy}\sigma(\yy)\ \dif s_\yy\\
&= -\frac1\rho^2 {\bf t}_\xx\cdot \int_\Gamma G(\zz-\yy){\bf t}_\yy \sigma(\yy)\ \dif s_\yy + 
({\bf t}_\xx \cdot \nabla_\zz)\int_\Gamma G(\zz-\yy)\frac{\partial \sigma(\yy)}{\partial s}\ \dif s_\yy.
\end{align}
%
Here ${\bf t}_\xx$ is the tangent vector at the point $\xx$ and $d/ds$ is the arclength derivative.
Letting $\zz\to\xx\in\Gamma$, we obtain
%
\begin{equation}
\frac{\partial}{\partial \nnu_\xx} \DD[\sigma](\xx) = -\frac1\rho^2 {\bf t}_\xx\cdot \SSS[\sigma{\bf t}](\xx) + \frac{\partial}{\partial s}\SSS\left[\frac{\partial \sigma}{\partial s}\right](\xx).
\end{equation}
%

%Suppose we split the solution to the screened Laplace boundary value problem~\eqref{eq:SL}
%into smooth portion $w_i$ and singular portion $u_i$. That is, 
%\begin{equation}
%w_i({\bf x}) = u({\bf x}) - u_i = u({\bf x}) - \int_{\Gamma_i }\left(\pderiv{}{\nnu_\yy}
%    K_0 \left(\frac{|\xx - \yy|}{\rho}\right)\right) \sigma_i(\yy) \,
%    \dif s_\yy, \quad \xx \in \Gamma_i.
%\end{equation}
%Consider the case when $f(u)=u^2$ in~\eqref{eq:free_energy}, we can rewrite the free energy functional as 
%
%\begin{align}
%\label{eq:free_energy2}
%  E[u(\xx)] &= C\rho \sum_{i=1}^{N_b}\int_{\Gamma_i} u \frac{\partial u}{\partial \nnu}  \,\dif s
%= C\rho\sum_{i=1}^{N_b}\int_{\Gamma_i} u \left(\frac{\partial w_i}{\partial \nnu}+\frac{\partial u_i}{\partial \nnu} \right) \, \dif s, \quad \xx\in\Gamma_i.
%\end{align}
%%%%
%Follow the divergence theorem on the last term in the equation above and denote $g_i(x)$ as the boundary data on $\Gamma_i$, we obtain
%\begin{align}
%\label{eq:free_energy3}
%  E[u(\xx)] &= C\rho\sum_{i=1}^{N_b}\left(\int_{\Gamma_i} u \frac{\partial w_i}{\partial \nnu} \,\dif s  + \int_{\mathbb{R}^n\setminus \overline{U}_i} \left( \nabla u \cdot\nabla u_i + u\Delta u_i\right) \,\dif \xx\right)\\
%%
%&= C\rho\sum_{i=1}^{N_b}\left(\int_{\Gamma_i} u \frac{\partial w_i}{\partial \nnu} \,\dif s  + \int_{\mathbb{R}^n\setminus \overline{U}_i} u\Delta u_i\,\dif \xx
%+\int_{\Gamma_i}\left(u+\frac12\sigma\right)\frac{\partial u_i}{\partial \nnu} \,\dif s     
%- \int_{\mathbb{R}^n\setminus \overline{U}_i} u\Delta u_i\,\dif \xx \right)\\
%&= C\rho\sum_{i=1}^{N_b}\left(\int_{\Gamma_i} u \frac{\partial w_i}{\partial \nnu} + 
%\left(g_i+\frac12\sigma_i\right)\frac{\partial u_i}{\partial \nnu}   \,\dif s \right), \quad \xx \in \Gamma_i.
%\end{align}
%
%
%

@@

Similar to shear flow simulations, we then place equilibrium states of all boundary conditions \eqref{eq:bcs} in a rotating Taylor-Green Flow
\begin{equation}
\uu_\infty(\xx) = V_0 \left(-\cos({\bf e}_x\cdot\xx)\sin({\bf e}_y\cdot\xx){\bf e}_x+\sin({\bf e}_x\cdot\xx)\cos({\bf e}_y\cdot\xx){\bf e}_y\right).
\end{equation}
%
The magnitude of the vortex flow is controlled by the velocity scale $V_0$.

\subsection{Steady-State Structure Confined in Narrow Channels}

@@

% Create the reference section using BibTeX:
\bibliography{reference}
